How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
a) 
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig6.pdf}
\caption{
a) Statistics from an ensemble of runs.
\label{fig6}
}
\end{figure*}
%---------------------------------------------------------%

>>>>

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig5.pdf}
\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
(a)--(b) Measurements of the longitudinal (a) and transverse (b) permeability are well separated with respect to the number of bodies, $M$. For each $M$, the mean and standard deviation of permeability are shown for increasing porosity (or time). (c) In all runs, the anisotropy grows substantially and reaches a maximum value of roughly 4--6. Runs with a large number of bodies ($M$ = 60, 80, or 100) show a second surge in anisotropy near the end of the simulation. (d)--(e) The configurational and shape contributions of anisotropy. While the shape anisotropy varies fairly regularly with time across all runs, the configurational anisotropy shows a distinct peak late in the simulation for runs with large $M$.
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.9 \textwidth]{./figs/fig6.pdf}
\caption{
Tortuosity statistics from an ensemble of simulations.
(a)--(b) The longitudinal (a) and transverse tortuosity measurements are well grouped with respect to the number of bodies. (c)--(e) Statistics of the ratio, $(T_2 -1)/(T_1 -1)$, including its configurational and shape contribution.
\label{fig6}
}
\end{figure*}
%---------------------------------------------------------%

Similar statistical analysis is performed on the tortuosity measurements and shown in Fig.~\ref{fig6}(a)--(b). Much like before, the tortuosity measurements are well separated by the number of bodies, with the error bars showing little overlap across different values of $M$. Measurements of the ratio, $(T_2 -1)/(T_1 -1)$, however, are not well grouped with respect to $M$, as seen in Fig.~\ref{fig6}(c).
